On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-08-17 Manuscript/manuscript.tex
Small Change
cleaning and edits

\begin{abstract}
Block bootstrap is widely used in constructing confidence intervals for
parameters estimated from stationary time series. Theoretically, the method
should provide valid confidence intervals as the length of the time series goes
to infinity. In practice, however, it is necessary to know how large of a finite
sample is required for block bootstrap confidence intervals to work well. This
study aims to answer this question in a simple simulation setting where the data
are generated from a first-order autoregressive process. The empirical coverage
rates of several commonly used bootstrap confidence intervals for the mean,
standard deviation, and the lag-1 autocorrelation are compared. In this 
study, we find that a large sample is needed to recover even a simple
parameter like the mean, and that the selection of interval type is very
important, especially in the case of the lag-1 autocorrelation, for which the coverage
deteriorates as the sample size increases when using Percentile, 
%Centered Bootstrap Percentile,
Bias-Corrected, or Bias-Corrected and Accelerated Bootstrap intervals.

\jy{put most
  notable findings here. Possibly 1) large sample is needed; percentile
  bootstrap is not working well for rho (can we offer some explanation?).}

@@

The necessary sample size for bootstrap standard errors to provide valid
uncertainty measures in practice has not been extensively studied. For
independent data and non-block bootstrap, \citet{hesterberg2015teachers} notes
that while percentile-based CIs for the mean \eds{for the mean? differences in means?} \mc{addressed} from 
nonparametric bootstrap
are more accurate than $t$-intervals for larger sample sizes, they are
less accurate for smaller sample sizes. \citet{chernick2009revisiting} finds 
that the best choice of method for estimating
the parameter of a distribution is dependent on the sample size, the number of
bootstrap resamples, and the confidence level. In the context of structural equation
modeling, \citet{nevitt2001performance} find
that a sample size of 200--1000 is usually sufficient for interval estimation
using standard nonparametric bootstrap. For dependent data, the necessary
sample
size for bootstrap is even less clear. In the setting of linear regression with a
focus on estimating the proportion of 
variation attributable to a certain variable, \citet{burch2012nonparametric} finds
that three nonparametric bootstrap methods (Standard, Percentile, and Bias-Corrected
and
Accelerated) approach the coverage of a pivotal quantity as $n$ gets larger for an
underlying normal distribution. However, they find that for other distributions, 
coverage may deteriorate as $n$ increases. 
When attempting to create interval estimations for the Pearson correlation 
coefficient of bivariate normal data, \citet{puth2015variety} find bootstrap 
methods to be less accurate than the Fisher's transformation method even 
for a sample of size $n = 100$ and correlation coefficient equivalent to 0.
Few studies have provided a practical guide on what size is needed
for block bootstrap inference for dependent data.
In a linear regression setting
with
dependent data where the
regression errors are generated from a homoscedastic AR(1) process, 
\citet{goncalves2005bootstrap} find that standard error
estimates from moving 
block bootstrap in small samples may be more accurate than
inference from closed-form asymptotic estimates, but moving block bootstrap 
\jy{did they do block or standard bootstrap?}
\mc{moving block bootstrap}
CIs still do not have sufficient coverage of the target parameter even for sample size
$n = 1024$.
\jy{I added more references to the reference folder that studied coverage of
  bootstrap CIs but not block bootstrap CIs.}

The goal of this paper is to provide some practical recommendations on
necessary sample size for block bootstrap with dependent data, similar to what 
was done for basic bootstrap in \citet{hesterberg2015teachers}. We consider a
simple situation of a stationary time series, where the parameters of
interests are the mean, standard deviation, and the first-order
autocorrelation coefficient. We compare six variants of block bootstrap
CIs from the literature \citep{diciccio1996bootstrap,
  rice2006mathematical}: a Standard Normal CI, and a Student's $t$ CI, a Percentile
Interval CI, 
%a Centered Bootstrap Percentile Interval, 
a Bias-Corrected CI, a Bias-Correct and Accelerated($BC_a$) CI, and a CI using a new
Proposed Method. Their
empirical coverage rates at different sample sizes and dependence levels are
compared in a simulation study. The results of this study suggest that
appropriate recovery of temporal dependence parameters is heavily dependent on
the type of interval used.

The remainder of the paper is organized as follows.
Section~\ref{sec:bbci} reviews block bootstrap procedures and how to use block
bootstrap estimates to construct CIs. Section~\ref{sec:simu} reports a
simulation
study comparing the coverage rates of the block bootstrap CIs. A discussion
concludes in Section~\ref{sec:disc}.

@@

@@

Alternatively, block-bootstrap can be done with overlapping or moving blocks.
Define moving blocks $Z_j = \{X_j, \ldots, X_{j + l - 1}\}$,
$j = 1, \ldots, n - l + 1$. Now we draw $k$ blocks from the $(n - l + 1)$
blocks
of $Z_j$'s with replacement and then align them in the order they were
picked
to form a block bootstrap sample. If $n$ is not a multiple of~$l$, the last
block selected will be reduced in size so that the final size of the
block bootstrap sample is $n$. It is also possible to implement moving block
bootstrap while allowing blocks to wrap around the end of the series. In other
words, define moving blocks (assuming $l > 1$) as:
\begin{equation}
Z_j =
    \begin{cases}
        \{X_j, \ldots, X_{j + l - 1}\}, & \text{if } j = 1, \dots, n - l + 1,\\
        \{X_j, \ldots, X_n, X_1, \ldots, X_{j-n+l-1}\}, & \text{if } j = n - l
        + 2 ,\dots, n.
    \end{cases}
\end{equation}
This version does not require that $n/l$ be an integer.
We used this version in this study as implemented in the function
\texttt{tsboot} from R package \textsl{boot} \citep{boot}.

@@

\jy{Read carpenter2000bootstrap and cite it; quite useful in sorting the literature}

\paragraph{Standard Normal CI}
Assuming that $\hat\theta_n$ is asymptotically normally distributed with
$\theta$ as the mean, we just need an estimate of the standard error to
construct an approximate CI \citep[p.168]{efron1993introduction}.
Let $\widehat{\text{SE}}$ be the empirical standard error of the block bootstrap
copies of $\hat\theta_n^{(b)}$, $b = 1, \ldots, B$. Let $z_{(\alpha)}$ be the $100\alpha$th percentile of the standard normal distribution.
A $(1 - \alpha)100\%$ standard normal CI is
\[
(\hat{\theta}_{n} - z_{(1-\alpha/2)}\widehat{\text{SE}}, \quad
\hat{\theta}_{n} - z_{(\alpha/2)}\widehat{\text{SE}}).
\]
\eds{define $z_{(.)}$ and check the signs} \mc{addressed}
This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.
Its validity relies on whether the distribution of $\hat\theta_n$ is reasonably
well approximated by its asymptotic normal distribution and whether the
bootstrap $\widehat{\text{SE}}$ approximates the true standard error.

\paragraph{Student's $t$ CI}
The procedure for constructing a Student's $t$ CI based on standard bootstrap is
described in \citet[p.158]{efron1993introduction}. \jy{give page or section number when
  citing a book} \mc{addressed} Let $t_{(\alpha, k)}$ be the $100\alpha$th percentile of the student's $t$ distribution with $k$ degrees of freedom.
With block bootstrapping, a $(1 - \alpha)100\%$ Student's $t$ CI is
\[
(\hat{\theta}_{n} - t_{(1-\alpha/2), k - 1}\hat{\text{SE}}, \quad
\hat{\theta}_{n} - t_{(\alpha/2), k -1}\hat{\text{SE}}),
\]
\eds{define $t_{(.)}$ and check the signs}  \mc{addressed}
where $k$ is the number of blocks.
This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.
Like the standard 
normal interval, the Student's $t$ CI is a table-based bootstrap interval
approach. In this case,
its validity relies on whether the distribution of $\hat\theta_n$ is
reasonably well approximation by the $t_{k-1}$ distribution with an
expected value of $\theta$, and whether the bootstrap 
$\widehat{\text{SE}}$ approximates the true standard error.

@@

%\paragraph{Centered Bootstrap Percentile CI}
%The procedure for constructing a Centered Bootstrap Percentile CI based on
%standard
%bootstrap is
%described in \citet{singh2008bootstrap}.
%The $(1 - \alpha)$ Centered Bootstrap Percentile CI is
%\[
%(2\hat{\theta}_{n} - \hat\theta_{n, 1 - \alpha/2}^{(b)}, \quad
%2\hat{\theta}_{n} - \hat\theta_{n, \alpha/2}^{(b)})).
%\]
%This CI is necessarily centered around the point estimator $\hat\theta_n$ and
%is asymmetric, as different critical values are used to compute
%the lower and upper bounds.

\paragraph{Bias Corrected ($BC$) Bootstrap CI}
The procedure for constructing a Bias Corrected Bootstrap CI based on standard
bootstrap is
described in \citet{carpenter2000bootstrap}.
Let $b = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$
for $b \in \{1, \ldots, B\}$. 
For a $(1 - \alpha)100\%$ CI, let
\[
\alpha_1 = \Phi(2b - z_{\alpha/2}).
\]
\[
\alpha_2 = \Phi(2b - z_{1 - \alpha/2}).
\]
A $(1 - \alpha)100\%~BC$ CI is
\[
(\hat\theta_{n, \alpha_1}^{(b)}, \quad \hat\theta_{n, \alpha_2}^{(b)}).
\]

\paragraph{Bias Corrected and Accelerated ($BC_a$) Bootstrap CI}
The $BC_a$ CI was first suggested in \citet{efron1987better}.
\jy{Isn't this just the empirical CDF? We just need the sample quantile functon.
  What is your reference for this description?}
Let $\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$
for $b \in \{1, \ldots, B\}$. 
Let $Z_{(i)}$ be the original sample without the $i$th block $z_i$, let
$\hat{\theta}_{(i)}$ be the jackknife values of $Z_{(i)}$
for $i \in \{1, \ldots, n\}$, 
and let $\hat{\theta}_{(.)} = \sum_{i=1}^{k} \hat{\theta}_{(i)} / k$. 
Let 
\[
\hat{a} = \frac{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^3}{6\{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^2\}^{3/2}}
.\] For a $(1 - \alpha)100\%$ CI, let
\[
\alpha_1 = \Phi\left(z_0 + \frac{z_{0} +
  z_{\alpha/2}}{1 - \hat{a}(z_{0} + z_{\alpha/2})}\right).
\]
\[
\alpha_2 = \Phi\left(z_0 + \frac{z_{0} +
  z_{1 - \alpha/2}}{1 - \hat{a}(z_{0} + z_{1 - \alpha/2})}\right).
\]
A $(1 - \alpha)100\%~BC_a$ CI is
\[
(\hat\theta_{n, \alpha_1}^{(b)}, \quad \hat\theta_{n, \alpha_2}^{(b)}).
\]
This CI is not necessarily centered by the point estimator $\hat\theta_n$. The
$BC_a$ method corrects for bias and skewness of the $B$ bootstrap point
estimates $\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including
bias-correction and acceleration factors. The acceleration factor refers to
the 
rate of change of of the standard error of $\hat\theta_n$ with respect to
$\theta$.

\paragraph{Proposed Method CI}
Our Proposed Method CI is centered at the point estimator and uses the
variation
in the bootstrap estimates to construct the error bound. This interval requires
the computation of $\bar\theta_n^{(b)}$, the mean of all bootstrap point
estimates, and $\widehat{\text{bias}} = \bar\theta_n^{(b)} - \hat\theta_n$.
A $(1 - \alpha)100\%$ CI using our Proposed Method is
\[
(\hat\theta_{n, \alpha/2}^{(b)} - \widehat{\text{bias}}, \quad
\hat\theta_{n, 1 - \alpha/2}^{(b)} - \widehat{\text{bias}}).
\]
This CI is necessarily centered around $\hat\theta_n$ and can also be rewritten
as 
\[
(\hat\theta_n + \hat\theta_{n, \alpha/2}^{(b)} - \bar\theta_n^{(b)}, \quad
\hat\theta_n + \hat\theta_{n, 1 - \alpha/2}^{(b)} - \bar\theta_n^{(b)}).
\]
and is asymmetric, as different critical values are used to compute
the lower and upper bounds.

@@

\jy{Explain what metric was used to compare their performances. That is, the
  coverage rates and how it was calculated. If a CI is valid, then the coverages
  rate is expected to match its nominal level.}

\jy{Make it flow better and conciser}
The coverage rates of the CIs were used to compare the performance of CIs. Let
$\hat\theta_{L, r}$ and $\hat\theta_{U, r}$ be the lower and upper bound,
respectively, for the confidence interval constructed for each replicate
$r \in \{1, \ldots, R\}$, where $R$ is the
number of replicates.
Then $cov = \#\{\hat\theta_{L, r} < \theta < \hat\theta_{U, r} \}/R$,  
for $r \in \{1, \ldots, R\}$.
If a CI method is valid, then the coverage rate is expected to match the
nominal 
level. Because it is unlikely for the coverage to exactly match the nominal
level,
we can construct a 95\% CI of the coverage
rate (which is an estimate of a proportion with $R = 10000$ \eds{R?} \mc{addressed}). If the
proportion
0.95 is included in the interval, the block bootstrap method is likely
performing
well. If all values in the interval are below 0.95, the results would suggest 
that the
method either is providing inaccurate estimation, is underestimating the
process' variability, or a combination of both. If all values in the interval
are above .95, the results suggest that the method is overestimating the
process' variability.

If $\theta$ is not covered at that $n$, a larger $n$ may be
necessary, assuming that performance will improve as $n$ is increased.
Remember that
the goal of this study is to find the smallest $n$ which is sufficient for
proper coverage.

The results are graphically displayed in Figures~\ref{fig:mu}--\ref{fig:phi};
these figures were generated using the R \textsl{ggplot2} package
\citep{ggplot2}.

@@

\jy{I'm curiouss why the coverge is so poor for the percentile method. Could
  plot 50 intervals for phi using different sample sizes?}

Based on Figure~\ref{fig:mu}, 
Student's $t$ CIs appear to have the highest \eds{largest?} \mc{addressed} coverage rates with 
respect 
to estimating $\mu$. In fact, for $\phi = -0.4$, Student's $t$ CIs over-cover 
$\mu$ for all sample sizes, whereas other CIs have coverage rates that
hover around the $95\%$ line at this level of $\phi$. For $\phi \geq -0.2$,
$BC_a$ CIs undercover $\mu$ for all $n$ observed. For $\phi = -0.2$, 
Standard, Percentile, %CBP, 
Proposed Method, and $BC$ CIs seem to 
generally cover $\mu$ at the nominal 
rate when $n \geq 400$. Student's $t$ CIs either recover or over-cover $\mu$
for $n \geq 100$. For $\phi = 0$, or when the 
sample is independently normally distributed, $n = 1600$ seems to 
be enough to recover $\mu$ when using Standard, Percentile, 
%CBP, 
Proposed Method, or $BC$ 
CIs. Student's $t$ CIs cover $\mu$ at the nominal rate for $n \geq 100$ at 
$\phi = 0$.
For $\phi = 0.2$, $n > 3200$ seems to be necessary to recover $\mu$
at the nominal level when using
any of the CIs, although some CIs, such as Student's $t$, are much closer to the
$95\%$ line than others, most notably $BC_a$.
For $\phi = 0.4$, a much larger sample size appears to be necessary. Once again,
Student's $t$ CIs are the closest to $95\%$ coverage, and $BC_a$ CIs are the 
furthest.

@@

These results beg the question of why certain methods perform poorly. To address 
this question, plots of 100 CIs using each of the Percentile, $BC$, and Proposed 
methods were constructed.

@@

As shown in Figure~\ref{fig:npi}, Percentile CIs appear to suffer from bias;
specifically, they seem to heavily underestimate $\phi$. $BC$ CIs do seem to correct this bias on average, but the width of
  the 
CIs is very inconsistent. We can see that the 
Proposed Method CIs correct the bias using 
$\widehat{\text{bias}} = \bar\theta_n^{(b)} -
  \hat\theta_n$, which seems to usually be negative, indicating a positive 
	correction from interval construction in Section~\ref{sec:bbci}.

@@

\jy{Discussion points:
  1) common practice on block bootstrap even for simple parameter such as the
  mean;
  2) further investigation needed for phi;
  3) impact on applied statsitics courses; student reactions (Dr. Schifano).
}

>>>>

\begin{abstract}
Block bootstrap is widely used in constructing confidence intervals for
parameters estimated from stationary time series. Theoretically, the method
should provide valid confidence intervals as the length of the time series goes
to infinity. In practice, however, it is necessary to know how large of a finite
sample is required for block bootstrap confidence intervals to work well. This
study aims to answer this question in a simple simulation setting where the data
are generated from a first-order autoregressive process. The empirical coverage
rates of several commonly used bootstrap confidence intervals for the mean,
standard deviation, and the lag-1 autocorrelation coefficient are compared.
A quite large sample is found necessary for the intervals to have the right
coverage rates even when estimaiting a simple parameter like the mean. Some
block bootstrap methods could fail when estimating the lag-1 autocorrelation.
It is surprising that the coverage property even deteriorates as the sample size
increases with some commonly used block bootstrap confidence intervals including
the percentile intervals and Bias-Corrected intervals.

@@

\jy{too wordy; do some condensing}
The performance of bootstrap standard errors with independent data
in providing valid uncertainty measures has been extensively studied.
For example, for non-block bootstrap, \citet{hesterberg2015teachers} notes
that while percentile-based CIs for the mean from nonparametric bootstrap
are more accurate than $t$-intervals for larger sample sizes, they are
less accurate for smaller sample sizes. \citet{chernick2009revisiting} finds 
that the best choice of method for estimating
the parameter of a distribution is dependent on the sample size, the number of
bootstrap resamples, and the confidence level. In the context of structural
equation modeling, \citet{nevitt2001performance} find
that a sample size of 200--1000 is usually sufficient for interval estimation
using standard nonparametric bootstrap. In estimating the proportion of 
variation attributable to certain variable, \citet{burch2012nonparametric} finds
that three nonparametric bootstrap methods (standard, percentile, and bias-corrected
and accelerated) approach the coverage of a pivotal quantity as the sample size
gets larger for an underlying normal distribution, but for other distributions, 
coverage may deteriorate even as the sample size increases.
When attempting to create interval estimations for the Pearson correlation 
coefficient of bivariate normal data, \citet{puth2015variety} find bootstrap 
methods to be less accurate than the Fisher's transformation method even 
for a sample of size of 100 and the correlation coefficientis equivalent to 0.
The general consensus is that a big sample size is necessary.

Few studies have provided a practical guide on what size is needed
for block bootstrap inference for dependent data.
In a linear regression setting with dependent data where the
regression errors are generated from a homoscedastic AR(1) process, 
\citet{goncalves2005bootstrap} find that the standard error estimates from
moving block bootstrap in small samples may be more accurate than those
from closed-form asymptotic estimates, but moving block bootstrap 
CIs still do not have sufficient coverage of the target parameter even for
sample size~$1024$.

The goal of this paper is to provide some practical recommendations on
necessary sample size for block bootstrap with dependent data, similar to what 
was done for basic bootstrap in \citet{hesterberg2015teachers}. We consider a
simple situation of a stationary time series, where the parameters of
interests are the mean, standard deviation, and the first-order
autocorrelation coefficient. We compare six variants of block bootstrap
CIs from the literature \citep{diciccio1996bootstrap,
  rice2006mathematical}: a standard normal CI, and a Student's $t$ CI,
a percentile CI, a bias-corrected CI, a bias-correct and accelerated ($BC_a$)
CI, and a CI proposed in this article. Their
empirical coverage rates at different sample sizes and dependence levels are
compared in a simulation study. The results of this study suggest that
appropriate recovery of temporal dependence parameters is heavily dependent on
the type of interval used.

The remainder of the paper is organized as follows.
Section~\ref{sec:bbci} reviews block bootstrap procedures and how to use block
bootstrap estimates to construct CIs; a simple CI obtained by recentering at the
point estimate is proposed for comparison. Section~\ref{sec:simu} reports a
simulation
study comparing the coverage rates of six???block bootstrap CIs. A discussion
concludes in Section~\ref{sec:disc}.

@@

\jy{Practice my writing style guidelines. Use two blank lines to separate
  paragraphs.}

@@

Alternatively, block-bootstrap can be done with overlapping or moving blocks.
Define moving blocks $Z_j = \{X_j, \ldots, X_{j + l - 1}\}$,
$j = 1, \ldots, n - l + 1$. Now we draw $k$ blocks from the $(n - l + 1)$
blocks
of $Z_j$'s with replacement and then align them in the order they were
picked
to form a block bootstrap sample. If $n$ is not a multiple of~$l$, the last
block selected will be reduced in size so that the final size of the
block bootstrap sample is $n$. It is also possible to implement moving block
bootstrap while allowing blocks to wrap around the end of the series. In other
words, define moving blocks (assuming $l > 1$) as:
\begin{equation}
Z_j =
    \begin{cases}
        \{X_j, \ldots, X_{j + l - 1}\}, & \text{if } j = 1, \dots, n - l + 1,\\
        \{X_j, \ldots, X_n, X_1, \ldots, X_{j-n+l-1}\}, & \text{if } j = n - l
        + 2 ,\dots, n.
    \end{cases}
\end{equation}
This version does not require that $n/l$ be an integer.

@@

\paragraph{Standard Normal CI}
Assuming that $\hat\theta_n$ is asymptotically normally distributed with
$\theta$ as the mean, we just need an estimate of the standard error to
construct an approximate CI \citep[p.168]{efron1993introduction}.
Let $\widehat{\text{SE}}$ be the empirical standard error of the block bootstrap
copies of $\hat\theta_n^{(b)}$, $b = 1, \ldots, B$. Let $z_{(\alpha)}$ be the
upper $\alpha$ quantile of the standard normal distribution.
A $(1 - \alpha)100\%$ standard normal CI is
\[
(\hat{\theta}_{n} - z_{(1-\alpha/2)}\widehat{\text{SE}}, \quad
\hat{\theta}_{n} - z_{(\alpha/2)}\widehat{\text{SE}}).
\]
This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.
Its validity relies on whether the distribution of $\hat\theta_n$ is reasonably
well approximated by its asymptotic normal distribution and whether the
bootstrap $\widehat{\text{SE}}$ approximates the true standard error.

\paragraph{Student's $t$ CI}
The procedure for constructing a Student's $t$ CI based on standard bootstrap is
described in \citet[p.158]{efron1993introduction}. Let $t_{(\alpha, k)}$ be the
upper $\alpha$ quantile of a $t$ distribution with $k$ degrees of freedom.
With block bootstrapping, a $(1 - \alpha)100\%$ Student's $t$ CI is
\[
(\hat{\theta}_{n} - t_{(1-\alpha/2), k - 1}\hat{\text{SE}}, \quad
\hat{\theta}_{n} - t_{(\alpha/2), k -1}\hat{\text{SE}}),
\]
\eds{define $t_{(.)}$ and check the signs}  \mc{addressed}
where $k$ is the number of blocks.
This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.
Like the standard 
normal interval, the Student's $t$ CI is a table-based bootstrap interval
approach. In this case,
its validity relies on whether the distribution of $\hat\theta_n$ is
reasonably well approximation by the $t_{k-1}$ distribution with an
expected value of $\theta$, and whether the bootstrap 
$\widehat{\text{SE}}$ approximates the true standard error.

@@

\paragraph{Bias Corrected ($BC$) Bootstrap CI}
The procedure for constructing a Bias Corrected Bootstrap CI based on standard
bootstrap is described in \citet{carpenter2000bootstrap}.
Let $b = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$
for $b \in \{1, \ldots, B\}$. Define
$\alpha_1 = \Phi(2b - z_{\alpha/2})$ and 
$\alpha_2 = \Phi(2b - z_{1 - \alpha/2})$.
A $(1 - \alpha)100\%~BC$ CI is
\[
(\hat\theta_{n, \alpha_1}^{(b)}, \quad \hat\theta_{n, \alpha_2}^{(b)}).
\]

\paragraph{Bias Corrected and Accelerated ($BC_a$) Bootstrap CI}
The $BC_a$ CI was first suggested in \citet{efron1987better}.
Let $\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$
for $b \in \{1, \ldots, B\}$. 
Let $Z_{(i)}$ be the original sample without the $i$th block $z_i$, let
$\hat{\theta}_{(i)}$ be the jackknife values of $Z_{(i)}$
for $i \in \{1, \ldots, n\}$, 
and let $\hat{\theta}_{(.)} = \sum_{i=1}^{k} \hat{\theta}_{(i)} / k$. 
Let 
\[
\hat{a} = \frac{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^3}{6\{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^2\}^{3/2}}.
\]
Define
\[
\alpha_1 = \Phi\left(z_0 + \frac{z_{0} +
  z_{\alpha/2}}{1 - \hat{a}(z_{0} + z_{\alpha/2})}\right)
\text{ and }
\alpha_2 = \Phi\left(z_0 + \frac{z_{0} +
  z_{1 - \alpha/2}}{1 - \hat{a}(z_{0} + z_{1 - \alpha/2})}\right).
\]
A $(1 - \alpha)100\%~BC_a$ CI is
\[
(\hat\theta_{n, \alpha_1}^{(b)}, \quad \hat\theta_{n, \alpha_2}^{(b)}).
\]
This CI is not necessarily centered by the point estimator $\hat\theta_n$. The
$BC_a$ method corrects for bias and skewness of the $B$ bootstrap point
estimates $\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including
bias-correction and acceleration factors. The acceleration factor refers to
the rate of change of of the standard error of $\hat\theta_n$ with respect
to~$\theta$.

\paragraph{A Proposed CI}
We propose a CI that is centered at the point estimator and uses the variation
in the bootstrap estimates to construct the error bound. This interval requires
the computation of $\bar\theta_n^{(b)}$, the mean of all bootstrap point
estimates, and $\widehat{\text{bias}} = \bar\theta_n^{(b)} - \hat\theta_n$.
A $(1 - \alpha)100\%$ CI is
\[
(\hat\theta_{n, \alpha/2}^{(b)} - \widehat{\text{bias}}, \quad
\hat\theta_{n, 1 - \alpha/2}^{(b)} - \widehat{\text{bias}}).
\]
This CI is centered around $\hat\theta_n$ and can also be rewritten
as 
\[
(\hat\theta_n + \hat\theta_{n, \alpha/2}^{(b)} - \bar\theta_n^{(b)}, \quad
\hat\theta_n + \hat\theta_{n, 1 - \alpha/2}^{(b)} - \bar\theta_n^{(b)}).
\]
It is asymmetric, as different critical values are used to compute
the lower and upper bounds.
\jy{Double check}

@@

The coverage rates of the CIs were used to compare the performance of CIs. Let
$\hat\theta_{L, r}$ and $\hat\theta_{U, r}$ be the lower and upper bound,
respectively, for the confidence interval constructed for each replicate
$r \in \{1, \ldots, R\}$, where $R$ is the
number of replicates.
Then $cov = \#\{\hat\theta_{L, r} < \theta < \hat\theta_{U, r} \}/R$,  
for $r \in \{1, \ldots, R\}$.
If a CI method is valid, then the coverage rate is expected to match the
nominal 
level. Because it is unlikely for the coverage to exactly match the nominal
level,
we can construct a 95\% CI of the coverage
rate (which is an estimate of a proportion with $R = 10000$. If the
proportion
0.95 is included in the interval, the block bootstrap method is likely
performing
well. If all values in the interval are below 0.95, the results would suggest 
that the
method either is providing inaccurate estimation, is underestimating the
process' variability, or a combination of both. If all values in the interval
are above .95, the results suggest that the method is overestimating the
process' variability.
Figures~\ref{fig:mu}--\ref{fig:phi} summarizes the empirical coverage rates and
the 95\% confidence intervals of the real coverage, generated using the R
\textsl{ggplot2} package \citep{ggplot2}.

@@

For estimating~$\mu$,
Student's $t$ CIs appear to have the highest coverage rates with respect 
to estimating~$\mu$. In fact, for $\phi = -0.4$, Student's $t$ CIs over-cover 
$\mu$ for all sample sizes, whereas other CIs have coverage rates that
hover around the $95\%$ line at this level of $\phi$. For $\phi \geq -0.2$,
$BC_a$ CIs undercover $\mu$ for all $n$ observed. For $\phi = -0.2$, 
Standard, Percentile, %CBP, 
Proposed Method, and $BC$ CIs seem to 
generally cover $\mu$ at the nominal 
rate when $n \geq 400$. Student's $t$ CIs either recover or over-cover $\mu$
for $n \geq 100$. For $\phi = 0$, or when the 
sample is independently normally distributed, $n = 1600$ seems to 
be enough to recover $\mu$ when using Standard, Percentile, 
%CBP, 
Proposed Method, or $BC$ 
CIs. Student's $t$ CIs cover $\mu$ at the nominal rate for $n \geq 100$ at 
$\phi = 0$.
For $\phi = 0.2$, $n > 3200$ seems to be necessary to recover $\mu$
at the nominal level when using
any of the CIs, although some CIs, such as Student's $t$, are much closer to the
$95\%$ line than others, most notably $BC_a$.
For $\phi = 0.4$, a much larger sample size appears to be necessary. Once again,
Student's $t$ CIs are the closest to $95\%$ coverage, and $BC_a$ CIs are the 
furthest.

@@

@@

These results beg the question of why certain methods perform poorly. To address 
this question, plots of 100 CIs using each of the Percentile, $BC$, and Proposed 
methods were constructed. As shown in Figure~\ref{fig:npi}, Percentile CIs
appear to suffer from bias; specifically, they seem to heavily underestimate
$\phi$. $BC$ CIs do seem to correct this bias on average, but the width of the
CIs is very inconsistent. Our proposed CIs correct the bias using 
$\widehat{\text{bias}} = \bar\theta_n^{(b)} -  \hat\theta_n$,
which seems to usually be negative, indicating a positive 
correction from interval construction in Section~\ref{sec:bbci}.

@@

\jy{Keep the tex source tidy. Clean it up.}
